---
title: "Quantitative SEM-EDS Fordefjorden"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(targets)
library(readxl)
library(writexl)
library(GGally)
library(ggrepel)
library(RColorBrewer)
library(factoextra)
library(patchwork)
library(see)
library(NbClust)
source("scripts/helper.R")
```

# Data treatment
```{r}
aSEM_reader <- function(xls, sheet) {
  #read in
  read_excel(
    xls,
    sheet = sheet,
    skip = 6,
    col_types = "text"
  ) %>%
    # clean and format
    rename_with( ~ str_replace(.x, " ", "_")) %>%
    select(Particle,
           Area,
           Length,
           Width,
           Aspect_Ratio,
           Equivalent_Diameter,
           Equivalent_Diameter,
           matches("\\b\\w{1,2}\\b")) %>%
    mutate(across(-1, ~ as.numeric(.x))) %>%
    mutate(across(-1, ~ replace_na(.x, 0)))
}

sp_addcluster_new <- function(in_df, cols, n_clusters = 0, vis = FALSE, npc = TRUE) {
  # cols selects columns used for clustering
  # if n_clusters == 0, shows optimal cluster number using three different methods.
  # otherwise performs kmeans clustering and adds the clusters to the data. Outputs either clustered data (vis == FALSE),
  # or plots of cluster compositions (vis == TRUE). NPC annotates n per cluster to output plot.
  
  set.seed(123)
  df <- in_df %>% select(matches(cols))
  
  if (n_clusters == 0) {
    p1 <- fviz_nbclust(df, kmeans, "silhouette", nboot = 500, k.max = 14)
    p2 <- fviz_nbclust(df, kmeans, "gap", nboot = 500, k.max = 14)
    p3 <- fviz_nbclust(df, kmeans, "wss", nboot = 500, k.max = 14)
    p1 + p2 + p3 + plot_annotation(caption = 'Different methods for determining optimal cluster size.',
                                   theme = theme(plot.title = element_text(size = 18)))
  }
  else {
    
    
    km.clusters <- kmeans(df,
                          n_clusters,
                          nstart = 100)$cluster %>%
      as_factor() %>%
      as_tibble() %>%
      rename(cluster = value)
    
    km.clusters <-
      cbind(in_df, km.clusters) %>% group_by(cluster) %>%
      mutate(n_per_clust = n()) %>% ungroup()
    
    if (vis == FALSE){
      
      km.clusters
      
    } else {
      
      p_out <- km.clusters %>% group_by(cluster) %>%
        pivot_longer(
          cols = matches("\\b\\w{1,2}\\b"),
          names_to = "element",
          values_to = "prop"
        ) %>% ungroup() %>%
        ggplot(aes(element, prop)) +
        geom_boxplot() +
        facet_wrap(~ cluster) +
        theme_bw() +
        theme(legend.position = "top")
      
      if (npc == TRUE) {
        p_out + geom_text(
      x = -Inf, y = Inf, hjust = 0, vjust = 1,
      aes(label = paste(" n = ", n_per_clust)), check_overlap = TRUE
    )
      } else {
        p_out
      }
    
     }
  }
}

dataset <- "files_imgs/sjovann_partikler_noytral.xls"

dataset_small <- "files_imgs/sjovann_minste_partikler_2.xls"

dataset_syre <- "files_imgs/sjovann_syre.xls" #acidified samples

ASEM_full <-
  aSEM_reader(dataset
    ,
    6
  )

ASEM_small <- aSEM_reader(dataset_small
    ,
    6)

ASEM_syre <- aSEM_reader(dataset_syre, 6)

```

# Methods
Dataset `r paste(dataset)` was used throughout, whereas `r paste(dataset_small)` was tested and resulted in lower sizes, yet still not abundant <250 nm particles. "Atomic % (norm)" data, sheet 6 in the excel file was used. (Total column was removed from raw data sheets "Wt % (norm.)" and "Atomic % (norm.) for consistency in the formatting of data during data exploration).

# Results and discussion

```{r cleaning}
# Removing O,C,Pt, removing particles that consisted only of these, then rescale, and remove particles below 1.5 um.
ASEM_clean <-
  ASEM_full %>%
  select(-O, -C, -Pt) %>%
  filter(Equivalent_Diameter < 1.5) %>%
  rowwise() %>%
  # selecting only the count variables in which more than trace levels present
  filter(mean(c_across(matches("\\b\\w{1,2}\\b"))) > 0) %>%
  ungroup() %>%
  rowwise() %>%
  # rescale appropriate variables
  mutate(across(matches("\\b\\w{1,2}\\b"), ~ .x / sum(c_across(
    matches("\\b\\w{1,2}\\b")
  )))) %>%
  ungroup() %>%
  filter(Na + Cl < 0.5, Cr < 0.5, Ni < 0.5) %>%
  select(-any_of(c("Cr", "Mo", "Ni", "P", "Pb", "S", "Zr")))

ASEM_clean_small <-
  ASEM_small %>%
  select(-O, -C, -Pt) %>%
  filter(Equivalent_Diameter < 1.5) %>%
  rowwise() %>%
  # selecting only the count variables in which more than trace levels present
  filter(mean(c_across(matches("\\b\\w{1,2}\\b"))) > 0) %>%
  ungroup() %>%
  rowwise() %>%
  # rescale appropriate variables
  mutate(across(matches("\\b\\w{1,2}\\b"), ~ .x / sum(c_across(
    matches("\\b\\w{1,2}\\b")
  )))) %>%
  ungroup() %>%
  filter(Na + Cl < 0.5, Cr < 0.5) %>%
  select(-any_of(c("Cr", "Mo", "Ni", "P", "Pb", "S", "Zr")))

ASEM_clean_syre <- ASEM_syre %>%
  select(-O, -C, -Pt) %>%
  filter(Equivalent_Diameter < 1.5) %>%
  rowwise() %>%
  # selecting only the count variables in which more than trace levels present
  filter(mean(c_across(matches("\\b\\w{1,2}\\b"))) > 0) %>%
  ungroup() %>%
  rowwise() %>%
  # rescale appropriate variables
  mutate(across(matches("\\b\\w{1,2}\\b"), ~ .x / sum(c_across(
    matches("\\b\\w{1,2}\\b")
  )))) %>%
  ungroup() %>% 
  filter(Na < 0.5, Cr < 0.5, F < 0.5) %>%
  select(-any_of(c("Cr", "Mo", "Ni", "P", "Pb", "S", "Zr", "F")))
```

## Overall size and atomic proportions

```{r proportions-total} 
#pivot appropriate vars for plot
p1 <- ASEM_clean %>%
  pivot_longer(
    cols = matches("\\b\\w{1,2}\\b"),
    names_to = "element",
    values_to = "prop"
  ) %>% ungroup() %>%
  # remove zeros for visibility of plot, minor elements
  filter(prop > 0) %>%
  ggplot(aes(x = element, y = prop)) +
  geom_violindot(
    fill_dots = "black",
    size_dots = 0.2,
    scale = "count",
    binwidth = 0.02,
    width = 2.5,
    fill = "grey"
  ) +
  labs(x = "Element", y = "Atomic proportion") +
  scale_fill_brewer(palette = "Paired") +
  theme_bw() + theme(legend.position = "none")+
    geom_text_repel(
      data = ASEM_clean %>%
        pivot_longer(
          cols = matches("\\b\\w{1,2}\\b"),
          names_to = "element",
          values_to = "prop"
        ) %>% filter(prop < 0.8, prop > 0) %>% group_by(element) %>%
        mutate(n_nps = n()) %>% distinct(prop %>% round(digits = 1), .keep_all = TRUE) %>% 
        filter(prop == quantile(prop, 0.9, type = 1)),
      aes(label = paste("n = ", n_nps, sep = ""), hjust = 0, vjust = 0, angle = 90), #nudge_x = 0.58,
      size = 3.5,
      ylim = c(0.3,0.76),
      segment.alpha = 0
    )
  

p2 <- ASEM_clean %>% filter(Equivalent_Diameter < 1.5) %>%
  mutate(Equivalent_Diameter = Equivalent_Diameter * 1000) %>%
  ggplot(aes(Equivalent_Diameter)) + geom_histogram(binwidth = 100, color = "black") +
  scale_x_continuous(breaks = seq(200, 1500, by = 100)) +
  theme_bw() +
  labs(x = expression(paste("Equivalent diameter [nm]", sep = "")), y = "Frequency [#]") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
  p1+p2+plot_layout(widths = c(1.3, 1))
  
  ggsave(filename = "out/SEM/fig8-A-B-ASEM-proportion-size.tiff", width = 18, height = 7, device='tiff', dpi=300, units = "cm")
```

Thus, Al is the most homogenous population among elements, mainly around 0.15-0.2 atomic proportion. Fe as major constituent (iron oxides) and lesser in many particles. Mn as manganese oxides and minor fraction. Also number of Ca-particles, not measured on sp-ICP-MS.

## Scatter plots

All elements in cleaned dataset:

```{r scatter-si}
ASEM_clean %>%
  select(matches("\\b\\w{1,2}\\b"), Particle) %>%
  pivot_longer(
    cols = matches("\\b\\w{1,2}\\b"),
    names_to = "element",
    values_to = "prop"
  ) %>%
  full_join(., ., by = "Particle") %>%
  rename(c(x = prop.x, y = prop.y)) %>%
  mutate(xy = x + y,
         xy = if_else(element.x == element.y, xy / 2, xy)) %>%
  # filter(element.x != element.y) %>%
  ggplot(aes(x = y, y = x, color = xy)) +
  geom_point(size = 1) +
  facet_grid(element.x ~ element.y, scales = "free") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.5), limits = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.5), limits = c(0, 1)) +
  labs(x = "Atomic proportion x", y = "Atomic proportion y") +
  scale_color_gradient(
   low = "lightblue", high = "black",
   guide = guide_colourbar(
     frame.colour = "black"
   )
 ) +
  labs(colour = "x + y")

ASEM_clean_syre %>%
  select(matches("\\b\\w{1,2}\\b"), Particle) %>%
  pivot_longer(
    cols = matches("\\b\\w{1,2}\\b"),
    names_to = "element",
    values_to = "prop"
  ) %>%
  full_join(., ., by = "Particle") %>%
  rename(c(x = prop.x, y = prop.y)) %>%
  mutate(
    xy = x + y,
    xy = if_else(element.x == element.y, xy / 2, xy)
  ) %>%
  # filter(element.x != element.y) %>%
  ggplot(aes(x = y, y = x, color = xy)) +
  geom_point(size = 1) +
  facet_grid(element.x ~ element.y, scales = "free") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.5), limits = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.5), limits = c(0, 1)) +
  labs(x = "Atomic proportion x", y = "Atomic proportion y") +
  scale_color_gradient(
    low = "lightblue", high = "black",
    guide = guide_colourbar(
      frame.colour = "black"
    )
  ) +
  labs(colour = "x + y")

```

Relevant elements, to paper:

```{r scatter}
ASEM_clean %>% filter(Si > 0 |
                        Fe > 0 | Al > 0 | Mn > 0) %>%
  select(Si, Fe, Al, Mn, Particle) %>%
  pivot_longer(
    cols = matches("\\b\\w{1,2}\\b"),
    names_to = "element",
    values_to = "prop"
  ) %>%
  full_join(., ., by = "Particle") %>%
  # filter(element.x != element.y) %>%
  rename(c(x = prop.x, y = prop.y)) %>%
  mutate(xy = x + y,
         xy = if_else(element.x == element.y, xy / 2, xy)) %>%
  # filter(element.x != element.y) %>%
  ggplot(aes(x = y, y = x, color = xy)) +
  geom_point(size = 1) +
  facet_grid(element.x ~ element.y, scales = "free") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.25), limits = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.25), limits = c(0, 1)) +
  labs(x = "Atomic proportion x", y = "Atomic proportion y") +
  scale_color_gradient(
   low = "lightblue", high = "black",
   guide = guide_colourbar(
     frame.colour = "black"
   )) +
  labs(colour = "x + y")
# mutate(across(.cols = matches("\\b\\w{1,2}\\b"), .fn = ~ na_if(.x, 0))) %>%
 ggsave(filename = "out/SEM/fig9-ASEM-scatter.tiff", width = 15, height = 12, device='tiff', dpi=300, units = "cm")

```

* x+y is the sum of different elements indicated.
* Al and Si are strongly correlated. Al does not occur without Si! K never without Si, (K almost always with Al and Si).
* Mn no correlation with Si or Al, but Fe.
* Fe correlated to Si, Mn, Al, but also alone.
* Si associated with all elements.

## SP-ICP-MS vs SEM: Aluminium

Only including `r ASEM_clean %>% filter(Equivalent_Diameter < 1.5) %>% select(Al, Si, Fe, Mn, Ca, K, Mg) %>% filter(Si > 0 | Fe > 0 | Al > 0 | Mn > 0 | Ca > 0 | Mg > 0 | K > 0) %>% filter(Al > 0) %>% nrow()` Al-containing particles  gives the scatter plot:
  
```{r}
ASEM_al <- ASEM_clean %>% filter(Al > 0)

# ASEM_al%>% ggpairs()+theme_bw()

ASEM_al %>% 
  pivot_longer(
    cols = matches("\\b\\w{1,2}\\b"),
    names_to = "element",
    values_to = "prop"
  ) %>%
  full_join(., ., by = "Particle") %>%
  rename(c(x = prop.x, y = prop.y)) %>%
  mutate(xy = x + y,
         xy = if_else(element.x == element.y, xy / 2, xy)) %>%
  # filter(element.x != element.y) %>%
  ggplot(aes(x = y, y = x, color = xy)) +
  geom_point(size = 1) +
  facet_grid(element.x ~ element.y, scales = "free") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90)) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.5), limits = c(0, 1)) +
  scale_y_continuous(breaks = seq(0, 1, by = 0.5), limits = c(0, 1)) +
  labs(x = "Atomic proportion x", y = "Atomic proportion y") +
    scale_color_gradient(
   low = "lightblue", high = "black",
   guide = guide_colourbar(
     frame.colour = "black"
   )) +
  labs(colour = "x + y")
```

Linear relationship between Si and K. Furthermore, Al-containing particles all have Si, with Si:Al ratios mostly 2.1 +-1:

```{r, include = FALSE}
ASEM_clean %>% filter(Al > 0) %>% ggplot(aes(Si/Al))+geom_histogram(binwidth = 0.1)+scale_x_continuous(breaks = seq(0,5, by = 0.2), limits = c(0.5,4))+ theme_bw()+theme(axis.text.x = element_text(angle = 90))

```


Al-containing particles are aluminum silicates. The Al:Si ratio is consistent with alkali feldspars such as orthoclase, which are the most abundant crustal mineral, and also dominant in the greywacke sandstone of the area.

Assuming the composition of orthoclase or anorthoclase (Na,K)AlSi~3~O~8~ yields the following size distribution for n = `r tar_read(size_dists_large) %>% filter(isotope == "Al", depth == 530, station == "Outer", measurement == 1) %>% nrow()` Al-particles as determined by SP-ICP-MS. The SEM data of `r ASEM_clean %>% filter(Al > 0) %>% nrow()` Al-containing particles yields the size distribution: 

```{r SEM-v-SP-Al}
p1 <- tar_read(size_dists_large) %>%
  filter(isotope == "Al", depth == 530, station == "Outer", measurement == 1) %>%
  # mutate(measurement = str_extract(sample_name, "m\\d")) %>%
  ggplot(aes(size_nm)) +
  geom_histogram(breaks = seq(50, 1550, by = 100), color = "black") +
  scale_x_continuous(breaks = seq(0, 1500, by = 100)) +
  theme_bw() + mytheme +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = "Diameter [nm]", y = "Frequency [#]")

p2 <- ASEM_clean %>% filter(Al > 0) %>%
  mutate(Equivalent_Diameter = Equivalent_Diameter * 1000) %>%
  ggplot(aes(Equivalent_Diameter)) +
  geom_histogram(breaks = seq(50, 1550, by = 100), color = "black")+
scale_x_continuous(breaks = seq(0, 1500, by = 100)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = expression(paste("Equivalent diameter [nm]", sep = "")),
       y = "Frequency [#]") +
  theme_bw()+mytheme+
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

p3 <- ASEM_clean_small %>% filter(Al > 0) %>%
  mutate(Equivalent_Diameter = Equivalent_Diameter * 1000) %>%
  ggplot(aes(Equivalent_Diameter)) +
  geom_histogram(breaks = seq(50, 1550, by = 100), color = "black")+
scale_x_continuous(breaks = seq(0, 1500, by = 100)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = expression(paste("Equivalent diameter [nm]", sep = "")),
       y = "Frequency [#]") +
  theme_bw()+mytheme+
    theme(axis.text.x = element_text(angle = 90, hjust = 1))

p1+p2

  ggsave(filename = "out/SEM/fig10-SP-ICP-v-SEM_Al-dia.tiff", width = 17, height = 6, device='tiff', dpi=300, units = "cm")

```

```{r}
# KS test
ks_ASEM <- ASEM_clean %>%
  filter(Al > 0) %>%
  mutate(Equivalent_Diameter = Equivalent_Diameter * 1000) %>% arrange(desc(Equivalent_Diameter))

ks_SP <- tar_read(size_dists_large) %>%
  filter(isotope == "Al", depth == 530, station == "Outer", measurement == 1) %>%
  mutate(Equivalent_Diameter = size_nm) %>% arrange(desc(Equivalent_Diameter))

ks.test(ks_ASEM$Equivalent_Diameter, ks_SP$Equivalent_Diameter,
  alternative = "two.sided"
)

```


Size effect of filter and magnification:

```{r}
  aSEM_reader(
    "~/OneDrive - Havforskningsinstituttet/Are Marine Nanoparticles/Paper_1_SW/SEM/211214_small_particles/sjøvann minste partikler 2.xls",
    6
  ) %>%
  select(-O,-C,-Pt) %>%
  filter(Equivalent_Diameter < 1.5, Al > 0) %>%
  rowwise() %>%
  #selecting only the count variables in which more than trace levels present
  filter(mean(c_across(matches("\\b\\w{1,2}\\b"))) > 0) %>%
  ungroup() %>%
  rowwise() %>%
  #rescale appropriate variables
  mutate(across(matches("\\b\\w{1,2}\\b"), ~ .x / sum(c_across(
    matches("\\b\\w{1,2}\\b")
  )))) %>% ungroup() %>% 
  filter(Na + Cl < 0.5, Cr < 0.5) %>%
    mutate(Equivalent_Diameter = Equivalent_Diameter*1000) %>% 
    ggplot(aes(Equivalent_Diameter))+
    geom_histogram(breaks = seq(50, 1550, by = 100), color = "black")+
scale_x_continuous(breaks = seq(0, 1500, by = 100)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(x = expression(paste("Equivalent diameter [nm]", sep = "")),
       y = "Frequency [#]", caption = "200 nm pore size, higher magnification.") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  theme_bw()
```


## Clusters

Using K-means clustering on `r ASEM_clean %>% nrow()` particles.

```{r cluster-diag}
#checking optimal cluster size, silhouette & gap
sp_addcluster_new(ASEM_clean, cols = "\\b\\w{1,2}\\b", n_clusters = 0)

#optional method, multiple methods:
# nb <- NbClust(ASEM_small_all_el %>% select(matches("\\b\\w{1,2}\\b")), distance = "euclidean", min.nc = 4,max.nc = 13, method = "kmeans", )

```

Optimal cluster size appear to be 5.   

```{r cluster}

#adding clusters
ASEM_clustered <- sp_addcluster_new(ASEM_clean, cols = "\\b\\w{1,2}\\b", n_clusters = 5)

```

### Overall   
Removed the least influencing elements for visualization.

```{r}
p1 <- sp_addcluster_new(ASEM_clean, cols = "\\b\\w{1,2}\\b", n_clusters = 5, vis = TRUE, npc = TRUE)+theme_bw() +
  theme(axis.text.x = element_text(angle = 90))+labs(x = "Element", y = "Atomic proportion")

p1

ggsave(filename = "out/SEM/si-fig11-overall_clust.tiff", width = 18, height = 9, device='tiff', dpi=300, units = "cm")


```

NaCl still abundant. Dominant clusters are silicates, Mn-oxides, Fe-oxides, Ca(Co3?) and Ca heteroaggregates/precipitates.

### Aluminum
Orthoclase: KAlSi3O8, density = 2.56. Mass fraction = 0.09694248
(Gibbsite, Al(OH)3, density = 2.42. Mass fraction = 0.3459231)

```{r}

ASEM_al_clustered <- sp_addcluster_new(ASEM_al, cols = "\\b\\w{1,2}\\b", n_clusters = 4)


sp_addcluster_new(ASEM_al, cols = "\\b\\w{1,2}\\b", n_clusters = 4, vis = TRUE)

# cluster 1 and 3 dominant
ASEM_al_clustered %>% group_by(cluster) %>% summarise(
  n_per_clust = n(),
  meanSi = mean(Si)/mean(Al),
  meanAl = mean(Al)/mean(Al),
  meanK = mean(K)/mean(Al),
  meanKNa = ((mean(K) + mean(Na) + mean(Ca) - mean(Cl)))/mean(Al)
)
```
No clear mineral classification possible, yet dominant 1 & 3 clusters are consistent with mixed phases or aggregates of feldspars.

## SP-ICP-MS vs SEM: Abundance

```{r}
tar_read(summarized) %>%
  filter(
    station == "Outer", measurement == "1", sampling == "Neutral", depth == 530,
    isotope %in% c("Al", "Fe", "Mn", "Si")
  ) %>%
  select(isotope, n_particles) %>%
  rename(c(element = isotope)) %>%
  mutate(Method = "SEM-EDS") %>%
  bind_rows(ASEM_clean %>%
    pivot_longer(
      cols = matches("\\b\\w{1,2}\\b"),
      names_to = "element",
      values_to = "prop"
    ) %>%
    ungroup() %>%
    # remove zeros for visibility of plot, minor elements
    filter(prop > 0) %>%
    group_by(element) %>%
    summarise(n_particles = n()) %>%
    filter(element %in% c("Al", "Fe", "Mn", "Si")) %>%
    mutate(Method = "SP-ICP-MS")) %>%
  pivot_wider(names_from = element, values_from = n_particles) %>%
  select(Method, Al, Fe, Mn, Si) %>%
  write_xlsx("out/SEM-v-SP_nparticles.xlsx")

```

## Agglomerative hierarchical clustering

* Dissimilarity euclidean
* Linkage average, complete and Ward's method
* Dendrogram cutoff element dependent.

```{r}
library(ComplexHeatmap)
library(dendsort)
library(dendextend)
library(gplots)
set.seed(123)

# hc.complete <- hclust(dist(ASEM_clean[,7:15]), method = "complete") %>% plot()
# hc.average <- hclust(dist(ASEM_clean[,7:15]), method = "average") %>% plot()

row_dend_avg = dendsort(hclust(dist(ASEM_clean[,7:15]), method = "average")) %>% as.dendrogram() %>% color_branches(k = 6)

row_dend_comp <- dendsort(hclust(dist(ASEM_clean[,7:15]), method = "complete")) %>% as.dendrogram() %>% color_branches(k = 6, groupLabels = TRUE)

row_dend_ward <- dendsort(hclust(dist(ASEM_clean[,7:15]), method = "ward.D2")) %>% as.dendrogram() %>% color_branches(k = 6)

row_dend_comp_syre <- dendsort(hclust(dist(ASEM_clean_syre[,7:13]), method = "complete")) %>% as.dendrogram() %>% color_branches(k = 2, groupLabels = TRUE)
  

hac_complete <- Heatmap(ASEM_clean[, 7:15],
  name = "Proportion",
  clustering_method_rows = "complete",
  row_dend_width = unit(5, "cm"),
  heatmap_width = unit(9, "cm"),
  show_column_dend = FALSE,
  cluster_rows = row_dend_comp,
  row_split = 6,
  row_gap = unit(2, "mm"),
  border = TRUE#,
  # left_annotation = rowAnnotation(
  #   foo = anno_block(gp = gpar(fill = "white"),
  #                    labels = c("1", "2", "3", "4", "5", "6"),
  #                    labels_rot = 0,
  #       labels_gp = gpar(col = "black", fontsize = 10)))
  )
hac_complete

hac_complete_syre <- Heatmap(ASEM_clean_syre[, 7:13],
  name = "Proportion",
  clustering_method_rows = "complete",
  row_dend_width = unit(5, "cm"),
  heatmap_width = unit(9, "cm"),
  show_column_dend = FALSE,
  cluster_rows = row_dend_comp_syre,
  row_split = 2,
  row_gap = unit(2, "mm"),
  border = TRUE#,
  # left_annotation = rowAnnotation(
  #   foo = anno_block(gp = gpar(fill = "white"),
  #                    labels = c("1", "2", "3", "4", "5", "6"),
  #                    labels_rot = 0,
  #       labels_gp = gpar(col = "black", fontsize = 10)))
  )
hac_complete_syre

svg(filename="hac_complete_syre_distribution.svg",width = 10, height = 5)
hac_complete_syre
dev.off()

# 
# Heatmap(ASEM_clean[,7:15],
#         name = "Average",
#         clustering_method_rows = "average",
#         row_dend_width = unit(10, "cm"),
#         heatmap_width = unit(15, "cm"),
#         show_column_dend = FALSE,
#         cluster_rows = row_dend_avg,
#         row_split = 6,
# )
# 
# Heatmap(ASEM_clean[,7:15],
#         name = "Ward",
#         clustering_method_rows = "ward.D2",
#         row_dend_width = unit(10, "cm"),
#         heatmap_width = unit(15, "cm"),
#         show_column_dend = FALSE,
#         cluster_rows = row_dend_ward,
#         row_split = 6
# )

hac_complete

# svg(filename="hac_complete_distribution.svg",width = 10, height = 5)
# hac_complete
# dev.off()

# ASEM_clean$cluster <- hclust(dist(ASEM_clean[,7:15]), method = "ward.D2") %>% cutree(k = 6) %>% as_factor()
# 
# ASEM_clean %>% ggplot(aes(x = cluster, y = Aspect_Ratio))+geom_boxplot()

```

